Group 5 Report

### 2022-08-03 Report/Group 5 report v2.Rmd
Bilder + La inn en "O"
Fixing YAML block

----
title: "Group 5 Report"
author: "ISSSV1337 Group 5"
date: "2022-08-03"
output:
  pdf_document: 
    toc: true
    highlight: pygments
    extra_dependencies: "subfig"
---

@@

ur data was gathered from OPXs own web page, and from Proff.no. As described 
in the previous parts, we wanted to gather data from the yearly reports or by 
scraping the Brønnøyund registry or Proff.no, but found this to be close to 
impossible. The data used is the one that OPX has gathered themselves directly 
from the organizations. This data was also used to test that our codes in R 
were correct.

>>>>

---
title: "Group 5 Report"
author: "ISSSV1337 Group 5"
date: "2022-08-03"
output:
  pdf_document: 
    toc: true
    highlight: pygments
    extra_dependencies: "subfig"
---

@@

Our data was gathered from OPXs own web page, and from Proff.no. As described 
in the previous parts, we wanted to gather data from the yearly reports or by 
scraping the Brønnøyund registry or Proff.no, but found this to be close to 
impossible. The data used is the one that OPX has gathered themselves directly 
from the organizations. This data was also used to test that our codes in R 
were correct.
